|

### 2023-05-01 manuscript/paper.Rmd
I added the manuscript in .rmd format.

# Exploratory Analysis

>>>>

# Data

```{r}
stickle <- read_csv('stickle_revamped.csv')

stick <- stickle %>% 
  mutate(gender = as.factor(case_when(
    grepl(".M.",univID,fixed=TRUE) ~ "Male",
    grepl(".F.",univID,fixed=TRUE) ~ "Female",
    grepl("Fos",univID,fixed=TRUE) ~ NA_character_
    )), ips = as.factor(ips)
  ) %>% 
  select(gender, everything())

#getting time vector, adding it to imputed data
univ <- stick %>% 
  mutate(time = as.integer(sub(".*([0-9]{2})\\..*", "\\1",univID)))
times <- univ %>% drop_na(time) %>% pull(time)

times_vector <- c(rep(1,43)) %>% 
  append(21-times)

#fossil n
fortab <- data.frame(time = 1:18, count = as.character(as.numeric((table(times_vector)))))
#knitr::kable(fortab)
#print(xtable(fortab),include.rownames = FALSE)
```

The data used here consists of a total of `r sum(!is.na(stick$gender))` extant specimens with known sex.  Of these, there are `r sum(stick$gender == "Female",na.rm = TRUE)` and `r sum(stick$gender == "Male",na.rm = TRUE)` female and male specimens, respectively.

In addition there are `r sum(is.na(stick$gender))` fossil specimens with unknown sex over 18 time periods. Table 1 shows the sample size at each of the 18 time periods.  There are at least 22 specimens at each time period with a high of 67 specimens in period 7.

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Mon May  1 11:20:28 2023 -->
\begin{table}[ht]
\centering
\begin{tabular}{rl}
  \hline
time & count \\ 
  \hline
  1 & 43 \\ 
    2 & 41 \\ 
    3 & 51 \\ 
    4 & 41 \\ 
    5 & 46 \\ 
    6 & 48 \\ 
    7 & 67 \\ 
    8 & 55 \\ 
    9 & 42 \\ 
   10 & 33 \\ 
   11 & 37 \\ 
   12 & 22 \\ 
   13 & 41 \\ 
   14 & 43 \\ 
   15 & 46 \\ 
   16 & 47 \\ 
   17 & 56 \\ 
   18 & 55 \\ 
   \hline
\end{tabular}
<!-- \label{tab1} -->
\caption{The number of stickleback fossils at each time point.  Sample size at each time point ranges from a low of 22 to a high of 67.}
\end{table}
